Comparing vector-based and ACT-R memory models of tag retrieval:\protect\\User-customized hashtag/tag prediction on Twitter and StackOverflow

### 2014-01-07 writeups/proposal/proposal.tex
merge
Former-commit-id: 43f6f39b37cf89e2cbbc0086dcf04447c68815d2 [formerly bacc4126246ca39f15aaeb9ced534ca8ab51f73f]
Former-commit-id: 45fc34c6172708076973a8e31fc9978e6aa22488

Although recent work has been done to model human tagging on the StackOverflow site, to our knowledge no vector-based holographic memory model has been tested or used.
I am curious to see the prediction difference between a vector-based model and current co-occurrence models on the StackOverflow dataset.
Both types of models are neurologically plausible, and both have been successfully incorporated as the declarative memory component of the ACT-R cognitive architecture \parencite{Rutledge2007}. 
Given that the Bayesian cognitively-plausible models have done so well to predict tag use on StackOverflow, it will be interesting to see how a cognitively-plausible vector-based model performs at the task.

>>>>

\textcite{Stanley2013} used an ACT-R inspired Bayesian memory model to predict human tagging on the StackOverflow site, but to our knowledge no vector-based holographic memory model has been tested or used.
Both types of models are neurologically plausible, and both have been successfully incorporated as the declarative memory component of the ACT-R cognitive architecture \parencite{Rutledge2007}. 
Given that the Bayesian cognitively-plausible models have done so well to predict tag use on StackOverflow, it will be interesting to see how a cognitively-plausible vector-based model performs at the task.
Prediction differences between the two models may help reveal ways where the constraints of each model can be adjusted in order to improve accuracy.
